Functional Pearl: Short and Mechanized Logical Relation for Dependent Type Theories

### 2024-02-26 paper/paper.tex
comment about intro. its not done yet

We hope our success at creating a short and mechanized proof for a
relatively feature-complete language will encourage future researchers
to leverage the tool of logical relations in mechanized
proofs for dependent types.
% % For
% % example, \citet{geuvers1994short} requires impredicativity to encode
% % Calculus of Constructions, an impredicative dependent type theory, but
% % also relies on the classification property to define the logical
% % relation over well-formed types and kinds. Their simple
% % presentation of the logical relation as an inductively defined
% % function over types, reminiscent of logical relations for simply typed
% % languages,

>>>>

We hope our success at creating a short and mechanized proof for a
relatively feature-complete language will encourage future researchers
to leverage the tool of logical relations in mechanized
proofs for dependent types.

\scw{TODO: this introduction is still not done. At this point, I think the
  first part has gotten a little long. We could say what we mean more
  concisely. We also need to work on the overview at the end of this section
  --- it need to be more descriptive about contributions and less of a table
  of contents.}

% % For
% % example, \citet{geuvers1994short} requires impredicativity to encode
% % Calculus of Constructions, an impredicative dependent type theory, but
% % also relies on the classification property to define the logical
% % relation over well-formed types and kinds. Their simple
% % presentation of the logical relation as an inductively defined
% % function over types, reminiscent of logical relations for simply typed
% % languages,
